---
title: "Sample dataset assignment"
output: html_notebook
author: Shubham Jagtap
date: "10/3/2019"
---

### Import data
importing [dataset](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/quakes.html) of Locations of Earthquakes in Fiji

**number of rows in data = 1000**

```{r ,echo=T}
# importing dataset of Locations of Earthquakes off Fiji

data <- quakes
head(data)

# info about the columns
# [,1]	lat =	numeric	Latitude of event
# [,2]	long =	numeric	Longitude
# [,3]	depth =	numeric	Depth (km)
# [,4]	mag =	numeric	Richter Magnitude
# [,5]	stations =	numeric	Number of stations reporting

```


This are the top10 highly affected places
```{r ,echo=T}
# importing libraries
pacman::p_load(tidyverse, dplyr, ggplot2,shiny, shinydashboard, leaflet, rvest,
               stringr, lubridate, rmarkdown, knitr)

top10mag <- data %>% top_n(10)  # max(data$mag) # to check the max value of mag.

# showing the top 10 max values of magnitude on leaflet map
leaflet(data = top10mag, options = leafletOptions(minZoom = 11)) %>%    
        addTiles("locations of seismic events in fiji since 1964") %>% 
        addMarkers(~long, ~lat, popup = ~as.character(mag), label = ~as.character(mag))

```
***

**Frequent questions based on the dataset**

1. Find the top affected places by the earthquakes and locate them on map.
2. Give the details of the depth, mag, stations in terms of following values.
    1. maximum
    2. minimum
    3. average
    4. locate all above values places on map.
3. Find the clusters of places according to the seismic events given in data.
4. Plot the various graph based on numeric values
    1. plot the Histogram, Boxplot, Voilin graphs
    2. scatter plot of depth and mag to show the relation between this values.


**Frequent questions other than dataset**

1. other information of those location such as
    1. Population, Geography/topography,rescue places for emergency situation, etc.
    2. Possibility of affecting other places because of one/more quakes situation.
    3. information about the quakes and seismic events at two major plate as mentione in details of the datahelp.

