---
title: "Sample dataset assignment 3"
author: "Shubham jagtap"
date: "10/3/2019"
output: html_notebook
---

### Import data
importing dataset of **On-time data for all flights that departed NYC in 2013.**

This dataset is taken fron one of the lectures of Hadley Wickham on [dplyr](https://dplyr.tidyverse.org/articles/dplyr.html).

**number of rows in data = 3,36,776**,
**number of variable columns = 19**

```{r, error=F}
# importing libraries
pacman::p_load(tidyverse, dplyr, ggplot2,shiny, shinydashboard,
               leaflet,stringr, lubridate, rmarkdown, knitr)

# library(nycflights13)
data <- nycflights13::flights

# nycflights13::weather   # for the weather data connection
# nycflights13::airlines  # for the airlines data connection
# nycflights13::airports  # for the airports data connection
# nycflights13::planes    # for the planes data connection
# nrow(data) 
head(data)
```

`colnames(data)`
`typeof(data)`
`summary(data)`
`str(data)`
`rownames(data)`

```{r}
colnames(data)

# code to nest or split by group (Please ignore)
# group_by(data, month) %>% nest(keep = T)
# group_split(data, month, keep = T)
# group_by(data, month) %>% group_nest(keep = T)
```

***

**Frequent questions based on the dataset**

1. Statistics of values per month (i.e. max, min, mean, total, percentage, etc) 
(only for the destination LAX,BWI,ROC,DCA,PHL,DAY,GRR,SMF,BZN,CHO)
    1. dep_delay, arr_delay, air_time, distance, etc
    2. flights count per origins, dest places.
    3. find out the most and least dep and arrival delay for month, carrier, dest and origin.

```{r}
statsset <- data %>% filter(dest== c('LAX','BWI','ROC','DCA','PHL','DAY','GRR','SMF','BZN','CHO'))
# statsset %>% filter(dest== 'BWI') # to check the data
# colnames(statsset) 
summary(statsset[c(6,9,15,16)]) # summary of data
#"dep_delay","arr_delay","air_time","distance"
data.frame(summary, row.names = T,check.rows = T,stringsAsFactors = T)
summary <- statsset %>% group_by(month=factor(month)) %>% select(6,9,15,16)
# unique(statsset$month)
colnames(summary)
summary %>% group_by(month) %>%  max()
summary <- tbl_df(summary)
summary %>% group_by(month) %>% apply(fun=max, na.rm=T)
# class(summary$dep_delay)
```


2. Visualization (only for the carrier YV, WN, US & B6)
    1. Prepare the scatterplot of dep_delay, arr_delay
    2. Histogram of statistics data as per month.
    3. Prepare verious plots. 

3. Regression and clustering models
    1. relation between dep_delay and arr_delay
    2. dep_ time vs dep_delay
    3. arr_time vs arr_delay
    4. distance vs airtime


**Frequent questions other than dataset**

1. merging the information of airlines, airports from the package and check the further analysis. use this information in visualizaion part.
